# 2014? Oregon Household Activity Survey (OHAS)

```{r build, eval = TRUE, echo = FALSE, results = "hide"}
build <- FALSE
```

```{r data, eval = build, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
TRIP <- read.table(file = "./../data/OHAS/2014-04-24/TRIP.csv", sep = ",", header = TRUE, row.names = 1)
PLACE <- read.table(file = "./../data/OHAS/2014-04-24/PLACE.csv", sep = ",", header = TRUE, row.names = 1)
HH <- read.table(file = "./../data/OHAS/2014-04-24/HH.csv", sep = ",", header = TRUE, row.names = 1)
PER <- read.table(file = "./../data/OHAS/2014-04-24/PER.csv", sep = ",", header = TRUE, row.names = 1)
ACTIVITY <- read.table(file = "./../data/OHAS/2014-04-24/ACTIVITY.csv", sep = ",", header = TRUE, row.names = 1)
LINKEDTRIP <- read.table(file = "./../data/OHAS/2014-04-24/LINKEDTRIP.csv", sep = ",", header = TRUE, row.names = 1)
LINKEDTRIP_PM<- read.table(file = "./../data/OHAS/2014-04-24/LINKEDTRIP_PM.csv", sep = ",", header = TRUE, row.names = 1)
TOUR <- read.table(file = "./../data/OHAS/2014-04-24/TOUR.csv", sep = ",", header = TRUE, row.names = 1)
VEH <- read.table(file = "./../data/OHAS/2014-04-24/VEH.csv", sep = ",", header = TRUE, row.names = 1)
VEHRET <- read.table(file = "./../data/OHAS/2014-04-24/VEHRET.csv", sep = ",", header = TRUE, row.names = 1)
```

```{r PLACE, eval = build, echo = FALSE, results = "hide"}
PLACE <- within(PLACE,{
    MODE <- factor(MODE)
})
```

```{r TRIP, eval = build, echo = FALSE, results = "hide"}
TRIP <- within(TRIP,{
    MODE <- factor(MODE)
})
```

```{r HH, eval = build, echo = FALSE, results = "hide"}
HH <- within(HH,{
    INCOME <- factor(INCOME)
    AREA <- factor(AREA)
})
```

```{r OHAS, eval = build, echo = TRUE, results = "show"}
OHAS <- list(
    PLACE = PLACE,
    HH = HH,
    PER = PER,
    VEH = VEH,
    VEHRET = VEHRET,
    ACTIVITY = ACTIVITY,
    TRIP = TRIP,
    TOUR = TOUR,
    LINKEDTRIP = LINKEDTRIP,
    LINKEDTRIP_PM = LINKEDTRIP_PM
)
```

```{r save, eval = build, echo = FALSE, results = "hide"}
saveRDS(OHAS, file = "./../data/OHAS/OHAS.rds")
```

```{r load, eval = !build, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
OHAS <- readRDS("./../data/OHAS/OHAS.rds")
```

The OHAS data came with four tables (_ACTIVITY_, _TRIP_, _TOUR_,
_LINKEDTRIP_) that were created with script _createTourTable.R_
written by Ben Stabler and Joel Freedman.  Presumably, the tables
_LINKEDTRIP_PM_ and _VEHRET_ are also tables created from the original
survey data.  I believe _PLACE_, _HH_, _PER_ and _VEH_ are the
original four tables.  Eric, Brendon, Kelly, please correct me if I am
wrong.

### Household Table
#### AREA, INCOME & RACE
```{r table, eval = TRUE, echo = FALSE, results = "show", warning = TRUE, error = TRUE, message = TRUE}
with(OHAS$HH,table(AREA))
with(OHAS$HH,table(INCOME))
with(OHAS$HH,table(RACE))
with(OHAS$HH,table(AREA,RACE, INCOME))
```

### Dimensions
```{r dim, eval = TRUE, echo = FALSE, results = "show", warning = TRUE, error = TRUE, message = TRUE}
lapply(OHAS, dim)
```

```{r summary, eval = FALSE, echo = FALSE, results = "hide", warning = TRUE, error = TRUE, message = TRUE}
lapply(OHAS, summary)
```
